Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-08 Documents/Paper/ms.tex
INS paper

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Various implementations of Nested Sampling exist, with different strategies
for sampling Equation~\ref{eq:constrained_prior}
\citep[e.g.][]{multinest, diamonds, radfriends}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space\footnote{
A C++ implementation of DNS, called {\tt DNest3}, is available at
{\tt https://github.com/eggplantbren/DNest3}}.

@@

>>>>

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Various implementations of Nested Sampling exist, with different strategies
for sampling Equation~\ref{eq:constrained_prior}, as well as other features
to infer whether the run was successful, or to improve the accuracy of
the marginal likelihood estimate
\citep[e.g.][]{multinest, importance, diamonds, radfriends}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space\footnote{
A C++ implementation of DNS, called {\tt DNest3}, is available at
{\tt https://github.com/eggplantbren/DNest3}}.

@@

\bibitem[Feroz et al.(2013)]{importance} Feroz, F., Hobson, M.~P., 
Cameron, E., Pettitt, A.~N.\ 2013.\ Importance Nested Sampling and the 
MultiNest Algorithm.\ ArXiv e-prints arXiv:1306.2144.
